A linear inside-outside algorithm for correcting sequencing errors in structured RNA sequences

### 2012-10-07 Recomb/conclusion_RECOMB.tex
conclusion
misc

In this article we presented a new and efficient way of
exploring the mutational landscape of an RNA, benefiting from the
 conserved consensus secondary structures  information,
to identify and fix sequencing errors. The algorithm runs in  $\Theta(n\cdot(|\Omega|+m^2))$ time and $\Theta(n\cdot(|\Omega|+m))$ memory, where $n$ is the length of the RNA,
$m$ the number of mutations and $\Omega$ the size of the multiple sequence alignment.

We additionally introduce a new
 pseudo energy model, both taking into account the nearest-neighbour energy model 
and, to account for geometrical discrepancies,  the isostericity of all base pairs.

By combining  into \texttt{RNApyro} these two approaches,  the 
mutational landscape exploration and the pseudo energy model,
 we created a tool predicting the positions
 yielding point-wise sequencing error and correcting them.
We validated our model with the 5s rRNA,
as presented in Sec.~\ref{sec:results}.
We observed that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
Importantly, the implementation is fast enough for practical applications.

@@

>>>>

In this article we presented a new and efficient way of exploring the mutational landscape of an RNA under structural constraints,
and apply our techniques to identify and fix sequencing errors. In adddition, we introduce a new
scoring scheme combining the nearest-neighbour energy model to new isostericity matrices in order to account for geometrical
discrepancies occurring during base pair replacements.
The algorithm runs in  $\Theta(n\cdot(|\Omega|+m^2))$ time and $\Theta(n\cdot(|\Omega|+m))$ memory, where $n$ is the length of the RNA,
$m$ the number of mutations and $\Omega$ the size of the multiple sequence alignment.

By combining  into \texttt{RNApyro} these two approaches,  the 
mutational landscape exploration and the pseudo energy model,
 we created a tool predicting the positions
 yielding point-wise sequencing error and correcting them.
We validated our model with the 5s rRNA,
as presented in Sec.~\ref{sec:results}.
We observed that the models
with larger weights on the
isostericity seems to hold a higher accuracy on the estimation of errors.
This indicates that an extractable signal is contained in the isostericity.
Importantly, the implementation is fast enough for practical applications.

@@

Further research, given the potential of error-correction of \texttt{RNApyro}, 
will evaluate its impact over large datasets with different existing
  NGS error-correction pipe-line.
